Prediction maps of defoliation at trees

### 2019-05-23 analysis/report-defoliation.Rmd
wflow_publish("analysis/report-defoliation.Rmd")

```{r echo = FALSE}
# rmarkdown::render(here("analysis/rmd/defoliation-maps.md"), 
#                   output_file = here("analysis/rmd/defoliation-maps.html"))
```

```{r echo = FALSE}
system("rsync -rlptDvzog --chown=www-data:www-data --fake-super /home/patrick/papers/2019-feature-selection/docs/report-defoliation.html -e ssh patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/"
       )
```

```{r echo = FALSE}
system("rsync -rlptDvzog --chown=www-data:www-data --fake-super \
  /home/patrick/papers/2019-feature-selection/docs/figure/defoliation-maps.Rmd/* \
  -e ssh patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/figure/report-defoliation.Rmd/"
)
```

>>>>

```{r echo = FALSE}
system("rsync -rlptDvzog --chown=www-data:www-data --fake-super \
  /home/patrick/papers/2019-feature-selection/docs/figure/defoliation-maps.Rmd/* \
  -e ssh patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/defoliation-maps/"
)
```
